The number of lattices of Voronoi's first kind

### 2014-06-06 findsuperbase/findsuperbase.tex
added start of java  to matlab code

As expected, all lattices generated in dimensions 1, 2, and 3 were found to be of Voronoi's first kind.  When $n=4$ roughly 25\% of the lattices generated by methods 1 and 2 were of Voronoi's first kind, but none of the 5000 bases generated by method 3 were of first kind for $n=4$.  When $n=5$ approximately 3\% of the lattices generated were of Voronoi's first kind for all 3 generation methods.  When $n=6$ less than 1\% of the lattices generated by methods 1 and 2 where of first kind and approximately 2\% of the lattices generated by methods 3 where of first kind.

@@

\begin{figure}[tp]
\centering 
  \begin{tikzpicture}
    \begin{axis}[ymode=log,font=\footnotesize,clip mode=individual,height=7cm,width=9cm,legend style={draw=none,fill=none,legend pos=south west,font=\footnotesize}]    
      \addplot[mark=*,color=red,only marks,/pgfplots/error bars/.cd,
        x dir=none,
        y dir=both,
        y explicit] table[x=n,y=proportion,y error=stddev] {code/data/uniform};
      \addplot[mark=square,color=blue,only marks,/pgfplots/error bars/.cd,
        x dir=none,
        y dir=both,
        y explicit] table[x=n,y=proportion,y error=stddev] {code/data/gaussian};
      \addplot[mark=x,color=green,only marks,/pgfplots/error bars/.cd, 
        x dir=none,
        y dir=both,
        y explicit] table[x=n,y=proportion,y error=stddev] {code/data/mimo};
\legend{Uniform, Gaussian, MIMO}
    \end{axis}
  \end{tikzpicture}
\caption{Estimated probability of generating a lattices of Voronoi's first kind for different basis distributions and dimension $n=1,2,3,4$.}
\end{figure}

>>>>

As expected, all lattices generated in dimensions 1, 2, and 3 were found to be of Voronoi's first kind.  When $n=4$ roughly 25\% of the lattices generated by methods 1 and 2 were of Voronoi's first kind, but none of the 5000 bases generated by method 3 were of first kind for $n=4$.  When $n=5$ approximately 2\% of the lattices generated were of first kind for all 3 generation methods.  When $n=6$ less than 1\% of the lattices generated by methods 1 and 2 where of first kind and approximately 1\% of the lattices generated by method 3 where of first kind.

@@

\begin{figure}[tp]
\centering 
  \begin{tikzpicture}
    \begin{axis}[ymode=log,font=\footnotesize,clip mode=individual,height=7cm,width=9cm,legend style={draw=none,fill=none,legend pos=south west,font=\footnotesize}]    
      \addplot[mark=*,color=red,only marks,/pgfplots/error bars/.cd,
        x dir=none,
        y dir=both,
        y explicit] table[x=n,y=proportion,y error=stddev] {code/data/uniform};
      \addplot[mark=square,color=blue,only marks,/pgfplots/error bars/.cd,
        x dir=none,
        y dir=both,
        y explicit] table[x=n,y=proportion,y error=stddev] {code/data/gaussian};
      \addplot[mark=x,color=green,only marks,/pgfplots/error bars/.cd, 
        x dir=none,
        y dir=both,
        y explicit] table[x=n,y=proportion,y error=stddev] {code/data/mimo};
\legend{Uniform, Gaussian, MIMO}
    \end{axis}
  \end{tikzpicture}
\caption{Estimated probability of generating a lattices of Voronoi's first kind for different basis distributions and dimension $n=1,2,3,4,5,6$.}
\end{figure}
